---
title: "The recipe of well-being"
# author: "Chiara Todaro"
date: "27 March 2019"
output: html_document
runtime: shiny
---
<style type="text/css">

h1.title {
  font-size: 30px;
  text-align: center;
}

h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 22px;
  font-family: "serif", Times, ;
  color: DarkGrey;
  text-align: right;
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache = TRUE)
```

```{r libraries}
library(shiny);library(leaflet);library(dplyr)
library(UsingR);library(RColorBrewer); library(ggplot2)

# path_app<-"./home/chiara/coursera/course9_Developing_Data_Products/assignment_interactive_map"
# shinyAppDir(
#   system.file(path_app, package="shiny"),
#   options = list(width = "100%", height = 700)
# )

```

In past years the 'well-being' of a country was only related to indicators of economic
growth such as Gross Domestic Product (GDP). More recently the opinion of the population
on social and personal aspects have been taken into account in order to have a deeper understanding of a country.

This development has been accomplished by [National Accounts of Well-being]("http://www.nationalaccountsofwellbeing.org"), by using surveys that capture
how people feel and experience their lives in their social environment.

This evolving research aims to bring about change in how societies shape the lives
of their citizens by making more self-aware decisions in the policy-making process.

### How 'well-being' can be quantified?

The indicator of well-being is not a well-defined quantity and for the
purpose of this representation it suffices to know that it takes in to account
both social and economic factors (see list below) and it is quantified in a
scale from 0 to 10.

List of factors used in well-being calculation:

      
* **GDP** :GDP per person (US$)
* **Equality** : % (GINI index) 
* **Food.consumption** : kCal per day per person
* **Alcohol.consumption** : litres per year per person
* **Energy.consumption** : kWh per year per person in residential electricity use
* **Family** : children per women
* **Working.hours** : per week per person (average)
* **Working.income** : hourly pay per person (US$)
* **Health.spending** : % of government spend
* **Military.spending**: % of GDP


```{r lefletmap_prep}
data("wellbeing")
wellbeing<- wellbeing %>% dplyr::select(Country,GDP,Equality,Food.consumption,Alcohol.consumption,
                                 Energy.consumption,Family,Working.hours,Work.income,
                                 Health.spending,Military.spending,Well.being)

countries<-wellbeing$Country;
capitalCoorLat<-c(48.207877, 50.849091, 42.690709, 35.188011, 55.675588, 59.439682, 60.188412,
                     48.856102, 52.517935, 47.493187, 53.349599, 52.367045, 59.913713, 52.227353,
                     38.722676, 48.147531, 46.059295, 40.418467, 59.326231, 46.948724, 50.461799,
                     51.504076);
capitalCoorLng<-c(16.378618, 4.356842, 23.331489, 33.382635, 12.567399, 24.744836, 24.945003,
                     2.353236, 13.401441, 19.026618, -6.259365, 4.913775, 10.752905, 21.000722,
                     -9.131732, 17.110453, 14.514914, -3.697429, 18.061721, 7.447394, 30.517915,
                     -0.114110);

capitals<-data.frame(lat=capitalCoorLat,lng=capitalCoorLng,wellbeingInd=wellbeing$Well.being)
pal_adhoc<-colorRampPalette(c("red","orange","green"))#brewer.pal(7,"Purples")
paletteWB<-colorNumeric(palette = pal_adhoc(7),domain = capitals$wellbeingInd);

```

<!-- Select a country to see which factors influence  the well-being measure. -->
```{r input_table_country,cache=FALSE}
# inputPanel(selectInput("country","Country:",
#                        c("Austria"=1,"Belgium"=2,"Bulgaria"=3,"Cyprus"=4,"Denmark"=5,
#                          "Estonia"=6,"Finland"=7,"France"=8,"Germany"=9,"Hungary"=10,
#                          "Ireland"=11,"Netherlands"=12,"Norway"=13,"Poland"=14,"Portugal"=15,
#                          "Slovakia"=16,"Slovenia"=17,"Spain"=18,"Sweden"=19,"Switzerland"=20,
#                          "Ukraine"=21,"United Kingdom"=22)
#                        )
#            )
```
               
               
```{r table_country,cache=FALSE}
# renderTable(t(wellbeing[input$country,]),rownames = TRUE,
#                                          bordered =TRUE, colnames = FALSE,
#          caption=" Data are taken from R package UsingR and more info can be found
#          <a href='http://prcweb.co.uk/lab/what-makes-us-happy/'> here</a> ")
```

The map below shows a measure of 'well-being' for 22 European countries.

**Click on the markers below to find out how much the well-being of each country is.**

```{r leaflet_map,cache=FALSE}
shinyApp(
   ui=fluidPage(
      column(8,
             tags$br(),
             leafletOutput("plot_map",width= "100%"), #,height = "100%"
             tags$br()
      ),
      column(4,
             helpText("Click on a circle to get info about the selected country"),
             tableOutput("table_country")
      )
   ),
   server = function(input, output,session){
      output$plot_map <- renderLeaflet({ #renderLeaflet
     plot_map<-capitals %>% leaflet() %>% addTiles() %>% 
        addCircleMarkers(lat=~lat, lng=~lng,weight=3,radius=capitals$wellbeingInd*1,
                         color= ~paletteWB(wellbeingInd), layerId=seq(nrow(capitals)),
                         popup=paste0("Well-being =",capitals$wellbeingInd)) %>% 
        addLegend("topright", pal = paletteWB, values= ~ wellbeingInd, title = "Well-being");
     plot_map
  })
  
  observeEvent(input$plot_map_marker_click, {
     click_id <- input$plot_map_marker_click$id
     output$table_country <- renderTable(t(wellbeing[click_id,]),rownames = TRUE,
                                         bordered =TRUE, colnames = FALSE,
         caption=" Data are taken from R package UsingR and more info can be found
         <a href='http://prcweb.co.uk/lab/what-makes-us-happy/'> here</a> ")
  })
   }
)
```


### How much each factor impacts on well-being?

A simple linear prediction model shows how much a unit change in each 
factor modifies, on average, the well-being measure.

In practice, coefficients can be seen as weights that balance 
the well-being measure. Positive coefficients increase the well-being, 
while negative ones drop it down. The graphical size of each coefficient 
represents the range of possible values it could take. The larger the 
circle, the larger the range. Note that this degree of uncertainty is 
intrinsical of the linear prediction model.

```{r lm_coeff}
fit<-lm(data=wellbeing,Well.being ~ .-Country)  
   CI<-confint(fit, rownames(summary(fit)$coefficients), level=0.95);
   CI<-CI[2:nrow(summary(fit)$coefficients),]
   Mcoef<-summary(fit)$coefficients[2:nrow(summary(fit)$coefficients),];
   dfCoef<-data.frame(coeff=Mcoef[,1],covar=rownames(Mcoef),ci2.5=CI[,1],ci97.5=CI[,2]);
   dfCoef<-dfCoef  %>% arrange(desc(coeff)) %>% mutate(cil=abs(ci97.5-ci2.5))
   
```


```{r plot_coeff,cache=FALSE}
renderPlot({
     pCoef<-ggplot(data=dfCoef,aes(y=covar,x=coeff))+ coord_flip()+ guides(size=FALSE)+
        geom_point(aes(size=cil,fill=covar),shape=21)+geom_vline(xintercept =0,colour="red")+ 
        theme(plot.title = element_text(hjust = 0.5,size=15),axis.text.x =element_blank())+ #,legend.position = "none"
        theme(axis.text.y=element_text(size=15),legend.key.size = unit(1, "cm"),
              legend.text = element_text(size = 15),legend.title = element_blank())+
        theme(axis.title=element_text(size=15))+
        labs(title = "Average Marginal Effects with confidence intervals")+
           ylab("per unit change in [see legend]")+xlab("linear coefficient")
     pCoef
})
```



### Can you find the perfect recipe for well-being?

The linear model coefficients allow us to predict the 
well-being by using new values of the factors listed above.
Note that this prediction model is for representative purposes 
only and it could take values outside the defined range 0-10.
                   
Move the sliders and find out the estimated well-being!
 
```{r table_prediction,cache=FALSE}
shinyApp(
   ui=fluidPage(
      column(4,
             sliderInput("sl_gdp","GDP",min = 1000, max = 100000, value = 30000,step=500),
             sliderInput("sl_equality","Equality",min = 0, max = 100, value = 60,step=5),
             sliderInput("sl_food","Food consumption",min=500,max=5000, value = 2000,step=20),
             sliderInput("sl_alcohol","Alcohol consumption",min=5,max=30,value = 20,step=1),
             sliderInput("sl_energy","Energy consumption",min=300,max=10000,value =3000,step=150)
      ),
      column(4,
             sliderInput("sl_family","Family",min = 1, max = 10, value = 4,step=1),
             sliderInput("sl_whours","Working hours",min = 1, max = 80, value = 40,step=1),
             sliderInput("sl_wincome","Work income",min = 1, max = 100, value = 30,step=5),
             sliderInput("sl_health","Health spending",min = 0, max = 100, value = 20,step=10),
             sliderInput("sl_military","Military spending",min = 0, max = 100, value = 5,step=10)
      ),
      column(4,
             tags$h5("The predicted well-being is* ...",align="center"),
             tags$head(tags$style(HTML("tbody>
                 tr:last-child {font-weight:bold;}"))
             ),
             tableOutput("prediction")
      )
   ),
   server = function(input,output,session){
      predictionTable<-reactive({
         newDF<-data.frame(Country="Austria",GDP=input$sl_gdp,Equality=input$sl_equality,
                           Food.consumption=input$sl_food,Alcohol.consumption=input$sl_alcohol,
                           Energy.consumption=input$sl_energy,Family=input$sl_family,
                           Working.hours=input$sl_whours,Work.income=input$sl_wincome,
                           Health.spending=input$sl_health,Military.spending=input$sl_military);
         mypred<-mutate(newDF,Well.being=predict(fit,newdata = newDF));
      })
      
      output$prediction<-renderTable(t(predictionTable()),rownames = TRUE,bordered =TRUE,
                                     colnames = FALSE,
                  caption="*Note that the name of the country is not relevant for calculations.")
   }
)

```

```{r footnote}
inputPanel(
   tags$img(src = "https://cran.r-project.org/Rlogo.svg", width = "100px", height = "100px"),
   tags$div(
   "Built in ",
   tags$a(href="https://www.rstudio.com/","RStudio"),
   "by C. Todaro with ",
   tags$a(href="https://cran.r-project.org/","R"),
   "packages shiny, leaflet, UsingR, dplyr, RColorBrewer, knitr, and ggplot2"
   ),
   tags$img(src = "https://www.rstudio.com/wp-content/uploads/2019/03/RStudio-Logo-Blue-Gray-125.png", width = "100px", height = "100px")
)
```


